### 2019-03-29 5_evaluation.tex
Some edits on section 5.

Figure~\ref{fig:flops} shows the FLOPS achieved with a compute-bound
kernel with varying problem sizes. This is the full version of
Figure~\ref{fig:flops-mpi}. In the best case, we measure peak FLOPS of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. For the purposes
of measuring efficiency we use our empirically determined number as
the baseline for 100\% efficiency.

@@

To answer this question, we use the METG metric to determine the
smallest task granularity which can be executed at a given level of
efficiency, as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench:

@@

% FIXME: talk about starpu and parsec?

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. For example, OpenMP
executes tasks via a thread pool, resulting in a form of work
stealing. This on-node work stealing, in combination with the task
parallelism due to the presence of 4 task graphs, is sufficient to
completely mitigate load imbalance. Systems that exploit task
parallelism but not work stealing on a node achieve lower peak
efficiency, but may achieve smaller task granularities as a result of
not relying on a shared global queue for tasks.

@@

Asynchronous systems such as Charm++ are able to show two benefits in
these plots. First, by overlapping communication with computation,
such systems are able to execute smaller task granularities at higher
levels of efficiency compared to the bulk synchronous MPI
implementation. Second, the asynchrony also makes the curves smoother,
as spikes in latency due to interference from other jobs can be
mitigated, leading to more predictable performance, especially at
smaller message sizes.

>>>>

Figure~\ref{fig:flops} shows the FLOPS achieved with a compute-bound
kernel with varying problem sizes. This is the full version of
Figure~\ref{fig:flops-mpi}. In the best case, we measure peak FLOPS of
$1.26 \times 10^{12}$, which compares favorably with the officially
reported number of $1.2 \times 10^{12}$ \cite{Cori}. For the purposes
of measuring efficiency, we use our empirically determined number as
the baseline for 100\% efficiency.

@@

To answer this question, we use the METG metric to determine the
smallest task granularity which can be executed at a given level of
efficiency, as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench. METG(50\%) is calculated
separately at each node count, to isolate runtime system behavior from
changes in communication latencies and topology when using
progressively larger portions of the machine. We consider the
following configurations of Task Bench:

@@

Implicitly parallel systems, such as PaRSEC, StarPU, and Regent, that
perform runtime analysis in order to build the DAG can suffer from
scalability bottlenecks if every node must consider the tasks
executing on all other nodes. PaRSEC DTD and StarPU mitigate this
partially be allowing the user to omit tasks that are not direct
dependencies of those executed on the current node. However, this DAG
trimming approach still requires some dynamic checks that scale with
the number of nodes. Approaches based on compile-time analysis can
partially or fully mitigate this overhead. PaRSEC PTG provides some
improvement over DTD by performing DAG expansion at compile time, but
still retains dynamic checks leading to limited scalability. Regent
uses a compile-time optimization that enables full horizontal
scalability~\cite{ControlReplication17}. A similar, manual
optimization is shown in the plots as PaRSEC DTD Shard.

% FIXME: remove parsec dtd shard if no space.

@@

The difference between the remaining systems is due primarily to the
scheduling behavior of the various systems. The execution of 4
simultaneous task graphs partially, but does not fully, mitigate the
load imbalance in the tasks. Therefore, systems which provide an
additional on-node work stealing capability see additional gains in
efficiency at large task granularities. However, the use of
work-stealing queues can also impact throughput at very small task
granularities. This can be seen in the difference between Chapel
Distrib (which uses a work stealing scheduler) vs Chapel with its
default (non-work-stealing) scheduler.

@@

Asynchronous systems such as Charm++ are able to show two benefits in
these plots. First, by overlapping communication with computation,
such systems are able to execute smaller task granularities at higher
levels of efficiency compared to the bulk synchronous MPI
implementation. Second, the asynchrony and scheduling flexibility from
executing multiple graphs also makes the curves smoother,
as spikes in latency due to interference from other jobs can be
mitigated, leading to more predictable performance, especially at
smaller message sizes.
